Kantian Patriots

### 2016-02-20 math_modeling/class/notes/classnotes.tex
mucho tarea

\section{The Game of Life}
The game of life is a mathematical model created by John Conway. The rules are as follows:
\begin{enumerate}
\item \underline{Birth Rule:} If at time $t$ a cell is dead (empty) and the cell has 3 live neighbors
in any direction, then at time $t+1$ the cell becomes alive.
\item \underline{Death Rule:} If at time $t$ a live cell has 0 and 1 neighbors it dies of isolation,
and if a live cell has 4 or more neighbors, it dies of overcrowding.
\item \underline{Survival Rule:} If at time $t$ a live cell has 2 or 3 live neighbors, then at time
$t+1$, the cell is still alive.
\end{enumerate}
\end{document}

>>>>

\section{The Game of Life}
The game of life is a mathematical model created by John Conway. The rules are as follows:
\begin{enumerate}
\item \underline{Birth Rule:} If at time $t$ a cell is dead (empty) and the cell has 3 live neighbors
in any direction, then at time $t+1$ the cell becomes alive.
\item \underline{Death Rule:} If at time $t$ a live cell has 0 and 1 neighbors it dies of isolation,
and if a live cell has 4 or more neighbors, it dies of overcrowding.
\item \underline{Survival Rule:} If at time $t$ a live cell has 2 or 3 live neighbors, then at time
$t+1$, the cell is still alive.
\end{enumerate}

\section{Tumor Growth}
Tumor growth can be modeled by the differential equation
\[
{dV\over dt} = aV^{2/3}-bV'.
\]
This equation arises from the logistic equation
\[
{dP\over dt} = P(a-bP),
\]
which has a solution of
\[
P={M\over 1+e^{-\log{be^c}-at}}.
\]
As $t\to\infty$, $P$ heads towards $M$, since the exponential decreases. The tumor equation can be solved
by separation of variables:
\begin{align*}
{dV\over aV^{2/3}-bV}&=dt\\
\int{dV\over aV^{2/3}-bV}&=\int dt\\
3\int{du\over a-bu}&=t+c.
\end{align*}
The previous result arises from the $u$-substitution where $u=V^{1/3}$. We can make another substitution,
where $w=a-bu$. Then
\begin{align*}
3\int{du\over a-bu}&=t+c\\
{-3\over b}\ln{|a-bu|}&=t+c\\
{-3\over b}\ln{|a-bV^{1/3}|}&=t+c.
\end{align*}
We now will specify the integration constant, $c$, in terms of the the volume of the tumor, $V$.
\begin{align*}
c &= t - {3\over b}\ln{|a-bV^{1/3}|}.
\end{align*}
The plot of this function can be expressed as
\[
t = {3\over b}\ln{|a-bV_{0}^{1/3}\over|a-bV^{1/3}},
\]
which simplifies to
\[
V = {e^{-bt}\left(-a+bV_{0}^{1/3}+ae^{bt/3}\right)^{3}\over b^{3}}
\]
This function's plot acts the same as the logistic equation.
\subsection{Gompertz Curve}
Gompertz Curve is an equation that arises from
\[
\begin{cases}
{dV\over dt}=r(t)V\\
{dr\over dt}=-Kr
\end{cases}.
\]
The model has the same curve that the logistic growth model has, but the equation differs.
\[
V=V_{0}^{r_{0}/k}e^{-(r_{0}/k)e^{-kt}}.
\]
The model can also be expressed as a single equation:
\[
\begin{cases}
{dV\over dt}=r(t)V\\
{dr\over dt}=-Kr
\end{cases}
\to
{dV\over dt} = aV-bV\ln{V},
\]
which has the solution
\[
V(t)=V_{0}e^{r_{0}/t}e^{-r_{0}/ke^{-kt}}
\]

\section{Voting}
{\centering
\begin{tabular}{c c c c c c}
22\% & 23\% & 15\% & 29\% & 7\% & 4\%\\
T&T&B&B&I&I\\
B&I&T&I&B&T\\
I&B&I&T&T&B
\end{tabular}
}
\noindent\\
Because of the plurality, T wins the election. If the I candidate is removed, then B wins the election.
Often in this model, we deal with non-transitive systems. Consider the following voter profile:\\
{\centering
\begin{tabular}{c c}
14 & $A>B>C$\\
12 & $C>A>B$\\
10 & $B>C>A$
\end{tabular}
}
\noindent\\
This profile has the following outcome:\\
{\centering
\begin{tabular}{l c c c}
First & A&C&B\\
Second & B&A&C\\
Third & C&B&A\\
& 14&12&10
\end{tabular}
}
\noindent\\
In this case, $A>B$, $B>C$, but $C>A$.

\subsection{Pairwise Comparison}
This is based on combinatorics; if we have 3 candidates, we have
\[
{3 \choose 2}
\]
possibilities.

\end{document}

### 2016-02-20 resume/work.tex
mucho tarea

\noindent\textbf{\large Work Experience}
\begin{enumerate}[label={\Roman*}.]
\item National Aeronautics and Space Administration $\Bigcdot$ November 2015 - Present
\begin{itemize}
\item Developed Android applications for Google Glass, Vuzix, and Recon Jet headsets
\item Used git extensively for version control
\item Wrote code primarily in Java
\end{itemize}
\item Freelance Application Developer $\Bigcdot$ July 2015 - Present
\begin{itemize}
\item Built a location based audio application called Audionce, written for Android and iOS.
\item Created a quiz web-application called WhensIt for the Public History Center at Christopher Newport
University
\item Built websites using JavaScript, HTML5, CSS3, and PHP
\end{itemize}
\item Christopher Newport University $\Bigcdot$ September 2013 - Present
\begin{itemize}
\item IT Customer Service Representative
\begin{itemize}
\item Aided customers with various software related IT issues
\item Assisted technicians with tasks such as installing hardware
\end{itemize}
\item Tutor for the Center for Academic Success
\begin{itemize}
\item Tutored several subjects including Mathematics, Computer Engineering, and Computer Science
\item Participated in both one on one tutoring and group tutoring
\end{itemize}
\end{itemize}
\item Kirk Family YMCA $\Bigcdot$ August 2009 - August 2015
\begin{itemize}
\item Lead Swim Instructor
\begin{itemize}
\item Managed a team of swim instructors that taught and oversaw various camps and lessons
\item Taught swimming lessons to children and adults of all ages
\item Promoted to manager in May 2015
\end{itemize}
\item Lifeguard
\begin{itemize}
\item Attended trainings for CPR and AED certifications, as well as First Aid and lifesaving skills
\item Worked to create and maintain a safe environment for all patrons of the pool by enforcing rules and
policies of the YMCA
\end{itemize}
\end{itemize}
\end{enumerate}

>>>>

\noindent\textbf{\large Work Experience}
\begin{enumerate}[label={\Roman*}.]

\item MyNewLeaf, LLC $\Bigcdot$ January 2016 - Present
\begin{itemize}
\item Contracted to develop Android version of iOS application
\item Collaborated with a large team of designers, managers, and programmers
\end{itemize}

\item National Aeronautics and Space Administration $\Bigcdot$ November 2015 - Present
\begin{itemize}
\item Developed Android applications for Google Glass, Vuzix, and Recon Jet headsets
\item Worked closely with a university professor to plan and create the application
\end{itemize}

\item Application Developer $\Bigcdot$ July 2015 - Present
\begin{itemize}
\item Contracted by MyNewLeaf to develop Android application
\item Worked on Augmented Reality application for NASA
\item Built a location based audio application called Audionce, written for Android and iOS.
\item Created a quiz web-application called WhensIt for the Public History Center at Christopher Newport
University
\item Built websites using JavaScript, HTML5, CSS3, and PHP
\end{itemize}

\item Christopher Newport University $\Bigcdot$ September 2013 - Present
\begin{itemize}
\item IT Customer Service Representative
\begin{itemize}
\item Aided customers with various software related IT issues
\item Assisted technicians with tasks such as installing hardware
\end{itemize}
\item Tutor for the Center for Academic Success
\begin{itemize}
\item Tutored several subjects including Mathematics, Computer Engineering, and Computer Science
\item Participated in both one on one tutoring and group tutoring
\end{itemize}
\end{itemize}

% \item Kirk Family YMCA $\Bigcdot$ August 2009 - August 2015
% \begin{itemize}
% \item Lead Swim Instructor
% \begin{itemize}
% \item Managed a team of swim instructors that taught and oversaw various camps and lessons
% \item Taught swimming lessons to children and adults of all ages
% \item Promoted to manager in May 2015
% \end{itemize}
% \item Lifeguard
% \begin{itemize}
% \item Attended trainings for CPR and AED certifications, as well as First Aid and lifesaving skills
% \item Worked to create and maintain a safe environment for all patrons of the pool by enforcing rules and
% policies of the YMCA
% \end{itemize}
% \end{itemize}
\end{enumerate}

### 2016-02-20 writing_in_ethics/paper_two.tex
mucho tarea

\title{Social Patriotism}
\begin{document}
\drafth{}
\inlinetitle
\begin{linenumbers}

Governmental power has drastically increased over the past decade. Much of the growth of power is due to acts of terrorism that have hugely impacted the nation. One of the most devastating acts of terrorism that the United States has seen is the attack on the world trade center on September 11, 2001. As a result, the government passed the USA PATRIOT act, also known as the Patriot Act. Many of the provisions in the Patriot Act grant the government the ability to avoid due process. Under the Patriot Act, the government is given excessive power to bypass the law; Kantian ethics provide an insight that can help determine whether or not use of the liberties granted to the government are ethically sound.

Section 6.6.6 of the text presents a situation in which a British news magazine, known as \textit{The Guardian}, published an article describing how the FBI indirectly requested that Verizon turn over all of its phone records. A key tenant of Kantian ethics is that others should never be used as a means to an end. The FBI's intention was never revealed, so it is hard to say whether or not they were using the phone records for personal gain or not. However, this fact alone is a breach of Kantian ethics; the FBI wanted to have access to private information, but refused to divulge the reason. Under the Categorical Imperative, moral actions should be able to be applied universally. The FBI did not release their private information, so, under the Categorical Imperative, the should not have taken others private information.

The power over communications granted to the FBI is greatly increased by the Patriot Act. Section 6.6.2 discusses the use of National Security Letters (NSLs), namely in regards to the Library Connection of Connecticut. In this scenario, the FBI used a provision of the Patriot Act to demand a user's browser history from a library computer. It follows from the argument made about the FBI requesting Verizon phone records that NSLs are a breach of Kantian ethics; the FBI prohibits individuals and companies that receive NSL's to reveal that the FBI had contacted them in the first place. This scenario differs from the Verizon scenario in that the FBI wanted the information of only one individual. The use of the NSL aside, the FBI's actions are still unethical under Kantian analysis. The agency requested that the Library Connection hand over information about another individual. In doing so, the FBI was using the Library Connection as a means to an end, which violates the Categorical Imperative. In this scenario, as well as the last, it is difficult to completely analyze the situations using Kantian analysis, since the FBI's intention is not actually know.

The third scenario presented by the text involves Brandon Mayfield, an attorney from Portland, Oregon. The FBI was presented with a partial fingerprint recovered from a terrorist attack in Spain that was linked back to Mayfield. The FBI then proceeded to investigate Mayfield, going as far as entering his home and seizing private information without proper legal authorization. This scenario differs from others in that the FBI's actions were directly aimed at Mayfield. They did not use anyone as a means to an end, as they did in other scenarios. However, they still violated Kant's Categorical Imperative. Kantianism focuses on the idea that moral laws should be able to be willed into universal laws, and as such, no party involved should be able to opt-out. Following this logic, Mayfield, as well as anyone else who wanted to, would be able to take information without legal basis from the FBI. This scenario differs from the previous two in that the FBI's intention is known. The agency sought to bring a suspected terrorist into custody. The methods used to reach that goal were not ethical however, which makes their actions unethical.

>>>>

\title{Kantian Patriots} \begin{document} \drafth{} \inlinetitle \begin{linenumbers}

Governmental power has drastically increased over the past decade. Much of the growth of power is
due to acts of terrorism that have greatly impacted the nation. One of the most devastating acts of
terrorism that the United States has seen is the attack on the World Trade Centers on September 11,
2001. As a result, the government passed the USA PATRIOT act, also known as the Patriot Act. Many of
the provisions in the Patriot Act grant the government the ability to avoid due process. Under the
Patriot Act, the government is given excessive power to bypass the law. Kantian ethics provide an
insight that can help determine whether or not use of the liberties granted to the government are
ethically sound.

Section 6.6.6 of the text presents a situation in which a British news magazine, known as
\textit{The Guardian}, published an article describing how the FBI indirectly requested that Verizon
turn over all of its phone records. A key tenant of Kantian ethics is that others should never be
used as a means to an end. The FBI's intention was never revealed, so it is hard to say whether or
not they were using the phone records for personal gain. However, this fact alone is a breach of
Kantian ethics; the FBI wanted to have access to private information, but refused to divulge the
reason. Under the first Categorical Imperative, moral actions should be able to be applied
universally. The FBI did not release their private information, so, under the Categorical
Imperative, they should not have taken others private information.

The power over communications granted to the FBI is greatly increased by the Patriot Act as well.
Section 6.6.2 discusses the use of National Security Letters (NSLs), namely in regards to the
Library Connection of Connecticut. In this scenario, the FBI used a provision of the Patriot Act to
demand a user's browser history from a library computer. It follows from the argument made about the
FBI requesting Verizon phone records that NSLs are a breach of Kantian ethics. the FBI prohibits
individuals and companies that receive NSL's to reveal that the FBI had contacted them in the first
place. The Categorical Imperative states that actions should be willed to universal laws, so it is
unethical to demand private information and to demand that their private information not be given
out. This scenario differs from the Verizon scenario in that the FBI wanted the information of only
one individual. The use of the NSL aside, the FBI's actions are still unethical under Kantian
analysis. The agency requested that the Library Connection hand over information about another
individual. In doing so, the FBI was using the Library Connection as a means to an end, which
violates the Categorical Imperative. In this scenario, as well as the last, it is difficult to
completely analyze the situations using Kantian analysis, since the FBI's intention is not actually
know.

The third scenario presented by the text involves Brandon Mayfield, an attorney from Portland,
Oregon. The FBI was presented with a partial fingerprint recovered from a terrorist attack in Spain
that was linked back to Mayfield. The FBI then proceeded to investigate Mayfield, going as far as
entering his home and seizing private information without proper legal authorization. This scenario
differs from others in that the FBI's actions were directly aimed at Mayfield. They did not use
anyone as a means to an end, as they did in other scenarios. However, they still violated Kant's
Categorical Imperative. Kantianism focuses on the idea that moral laws should be able to be willed
into universal laws, and as such, no party involved should be able to opt-out. Following this logic,
Mayfield, as well as anyone else who wanted to, should be able to take information without legal
authorization as the FBI did. This scenario differs from the previous two in that the FBI's
intention is known. The agency sought to bring a suspected terrorist into custody. The methods used
to reach that goal were not ethical however, which makes their actions unethical.
